\documentclass[12pt]{amsart}
\usepackage{amsaddr}
\usepackage[draft]{../marktext} 
%% Remove draft for real article, put twocolumn for two columns
\usepackage[draft]{../svmacro}
\usepackage[utf8]{inputenc}
%\usepackage{lineno}
\usepackage[style=alphabetic, backend=biber]{biblatex}
\addbibresource{../bibliography.bib}

%% commentary bubble
\newcommand{\SV}[2][]{\sidenote[colback=green!10]{\textbf{SV\xspace #1:} #2}}

%% Title 
\title{ MATH 312: Midterm }
\author{Name: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_}
\address{}

%\author{Co-author}
%\address{  }
%\email {  }
%
\date{\today}

\begin{document}

%\linenumbers
\maketitle


\section*{Instructions}

\begin{enumerate}
	\item Pick 5 out of 6 questions to do. Specify your choices. If you don't I'll take the minimum of all possible points.
	\item Show your work, be as thorough as possible.
	\item You have 80 minutes
\end{enumerate}


\newpage

\begin{question}[Quick questions, 5 points each] Complete the following:
	\begin{enumerate}
		\item Give the definition of a topological space.
		      \vspace{7cm}

		\item Give the definition of a measure space (include definitions of sigma algebra and measure).

		      \vspace{7cm}
		\item Give an example of a topological space where every set is a clopen set.

		      \vspace{7cm}
		\item What does it mean for a set to be compact in a topology?

		      \vspace{7cm}
		\item What is a continuous function from $(X, \tau_X)$ to $(Y, \tau_Y)$?
		      \vspace{7cm}
	\end{enumerate}
\end{question}

\newpage

\begin{question}[True or False? Justify. 20 points.]
	A set $K$ in a topological space $(X, \tau)$ is closed if it is compact.

\end{question}
\newpage

\begin{question}[True or False? Justify. 20 points.]
	A closed subset of a compact set is compact.
\end{question}
\newpage

\begin{question}[True or False? Justify. 20 points.]
	Let $f: (X, \tau_X) \to (Y, \tau_Y)$ be continuous.
	If $K$ is compact, then $f(K)$ is compact.
\end{question}

\newpage
\begin{question}[20 points]
	Let $(X, \tau_X)$ and $(Y, \tau_Y)$ be topological spaces where $Y$ is compact.
	If $N$ is an open set of $X\times Y$ containing the slice $\set{x_0} \times Y$ of $X \times Y$.
	Prove that there exists a neighborhood $W$ of $x_0$ such that $W\times Y \subseteq N$.
\end{question}

\newpage
\begin{question}[20 points] Complete the following:
	\begin{enumerate}
		\item Let $c_{nj}$ be non-negative real numbers that increase in $n$ to $c_j$ for each $j$.
		      Suppose $\sum_{j=1}^\infty c_j < \infty$, show
		      \begin{equation*}
			      \lim_{n\to \infty} \sum_{j=1}^\infty c_{nj} = \sum_{j=1}^\infty c_j \,.
		      \end{equation*}

		\item (True or False? Justify)
		      Let $\mu_1, \mu_2, \dots$ be probability measures
		      on a measurable space $(X, \mathcal{A})$, that is $\mu_n (X) = 1$ for all $n \in \N$.
		      Suppose that $\mu_n (A)$ is increasing for each $A \in \mathcal{A}$.
		      Define
		      \begin{equation*}
			      \mu(A) = \lim_{n\to \infty} \mu_n(A) \,.
		      \end{equation*}
		      Then, $\mu$ is a measure on $(X, \mathcal{A})$.
	\end{enumerate}
\end{question}

\end{document}
