\documentclass[12pt]{amsart}
\usepackage{amsaddr}
\usepackage[draft]{../marktext} 
%% Remove draft for real article, put twocolumn for two columns
\usepackage[draft]{../svmacro}
\usepackage[utf8]{inputenc}
%\usepackage{lineno}
\usepackage[style=alphabetic, backend=biber]{biblatex}
\addbibresource{../bibliography.bib}

%% commentary bubble
\newcommand{\SV}[2][]{\sidenote[colback=green!10]{\textbf{SV\xspace #1:} #2}}

%% Title 
\title{ MATH 312: Homework 2 }
\author{}
\address{}

%\author{Co-author}
%\address{  }
%\email {  }
%
\date{\today}

\begin{document}

%\linenumbers
\maketitle



\printbibliography

In all the questions below, show your work.

\begin{question}
	Show that every metric space is normal.
\end{question}

\begin{question}
	Show that every compact Hausdorff space is normal.
\end{question}

\begin{question}
	Let $\set{f_n: K \to \R}_{n\in \N}$ be a sequence of $L$-Lipschitz functions where $K \subset \R$ is a compact set.
	Show that $\set{f_n}$ is equicontinuous.
\end{question}

\begin{question}
	Prove/disprove the following statement:
	the sequence of functions $f_n: \R \to \R$ defined by
	\begin{equation*}
		f_n(x) = \cos(n + x) + \ln \left( 1 + \frac{1}{n + 2} \sin^2 (n^n x) \right)
	\end{equation*}
	is equicontinuous.
\end{question}


\begin{question}
	Let $(M,d)$ be a metric space.
	A family of functions $\cF$ mapping from $M \to \R$ is said to be pointwise equicontinuous if for
	every $x \in M$ and $\epsilon > 0$ there exists $\delta_x >0$ such that
	for every $f \in \cF$,
	$\abs{f(x) - f(y)} < \epsilon$ whenever $d(x,y) < \delta_x$.

	Suppose that every pointwise equicontinuous sequence of  functions $M \to \R$
	is uniformly equicontinuous.
	Does this mean $(M,d)$ is a compact metric space?
\end{question}

\begin{question}
	A continuous, strictly increasing function $\mu: (0,\infty) \to (0,\infty)$
	is called a \emph{modulus of continuity} if $\mu(s)\to 0$ as $s\to 0$.
	A function $f:[a,b]\to \R$ has modulus of continuity $\mu$ if
	$\abs{f(s) - f(t)} \leq \mu(\abs{s-t})$ for all $s,t\in [a,b]$.
	Prove
	\begin{enumerate}
		\item A function is uniformly continuous if and only if it has a modulus
		      of continuity.
		\item A family of functions is equicontinuous if and only if its members have
		      a common modulus of continuity.
	\end{enumerate}
\end{question}


\begin{question}
	(Challenging)
	Given $\lambda \in (0,1)$, a function $u_\lambda: B(0,1) \subseteq \R \to \R$
	is said to be a solution to a  static discount
	Hamilton-Jacobi equation\footnote{This equation is fundamental in optimal control theory and all kinds of engineering}
	on the ball $B(0,1) \subseteq \R$
	\begin{equation*}
		\lambda  u_\lambda(x) + H( u'_\lambda(x)) = 1 \quad \text{ when } x\in B(0,1) \,.
	\end{equation*}
	Here, $u'_\lambda$ denotes the derivative of $u_\lambda$.
	The function $H: \R \to \R$ is a continuous function called the Hamiltonian of the equation and typically has the following property
	\begin{equation}
		\label{H}
		\lim_{\abs{p} \to \infty} H(p) = \infty\,.
		\tag{H}
	\end{equation}
	Suppose magically that you know that there exists a number $M >0$ such that
	for every $\lambda \in (0,1)$,
	\begin{equation*}
		\norm{u_\lambda}_\infty \leq M\,.
	\end{equation*}
	Assuming~\eqref{H},
	show that the family $\set{u_\lambda}$ is uniformly equicontinuous.

	Deduce then there exists a function $\bar u$ such that for some subsequence
	$\lambda_j \to 0$ as $j\to \infty$,
	\begin{equation*}
		\lim_{j\to \infty} \norm{u_{\lambda_j} - \bar u}_\infty = 0\,.
	\end{equation*}
	Guess  (NO PROOF\footnote{A proof for this fact will result in an automatic A+ in this class}) the equation for $\bar u$.
\end{question}

\end{document}
